### 2016-03-09 paper/algorithm.tex
yasu

Assume that we have $N$ threads $\{T_i | i=1, 2, \cdots, N\}$.  Alpha
expansion picks one label in each iteration to perform fusion. FM
invokes one proposal generation scheme and generate a solution proposal
for fusion. Swarm Fusion has 1) a {\it proposal pool}, from which we can pick
arbitrary number of proposal generation schemes and generate proposals,
and 2) a {\it solution pool}, from which we can pick arbitrary number of
intermediate solutions generated by all the other threads.
%
% Traditional FM has a set of proposal generation schemes to be
% invoked
%
% There are two places to
% collect solutions or solution proposals for fusion. First, the {\it
% proposal pool} can generate new solution proposals on request.
% %
% Second, the {\it solution pool} stores the solutions that have been
% fused by the threads.
In our base configuration, the solution pool only remembers one (the
best) solution generated by each thread, but the scheme can be more
general.

Swarm Fusion has two main parameters $\alpha_i$ and $\beta_i$ (for each thread
$T_i$), determining the processing flow of the algorithm: In each fusion
step, the thread collects $\alpha_i$ solution proposals from the
proposal pool and $\beta_i$ solutions from the solution pool.
%
One can further customize how to pick certain proposal generation
schemes (as in ~\cite{delong}) or solutions. Swarm Fusion framework is
very flexible and yields various architecture as shown in
Figure~\ref{fig:model}.
%
The bottom right configuration is the most general one, in which we
always fuse some solution proposals and some concurrent solutions. This
is a multi-way fusion (not binary) with a non-submodular energy, and we
use TRW~\cite{kolmogorov} for the fusion. Of course, if one knows that a
certain fusion step is a binary fusion with submodular energy, one can
use graph-cuts instead~\cite{alpha_expansion_paper}. If a certain fusion
step is a binary fusion with non-submodular energy, one can use
QPBO~\cite{second_order_smoothness_stereo}.
%
Note that the threads are all synchronized in the figure for a
illustration purpose. In practice, all the threads run asynchronously
with a (read-write) lock on the data in the solution pool. The
asynchronous processing could be difficult for cloud parallel computing.
%
\begin{figure}[tb]
 \includegraphics[width=\columnwidth]{figure/model.pdf} \caption{Swarm
 Fusion architecture and its relationships to existing methods.
}\label{fig:model}
\end{figure}
%
%

%

@@

\noindent
abc

Five architectures.

Sequential.
Naive parallel sequential (viktor).
H-fusion (veksler, delong)
Ours (sharing solutions)
Ours (multiple proposals)
Ours (multiple proposals and sharing solutions)

\mysubsubsection{Base architecture}
The swarm fusion is highly flexible, and we first introduce our base
architecture that exploits general strenghts offered by the
framework. Later, we explain how to further optimize the configuration
to boost performance for specific problems. In the base architecture,
all the threads fuse some number of proposals from the proposal pool and
some number of solutions from the solution pool in each step. In other
words, all the threads constantly exchange solutions while injecting new
proposals. This architecture is illustrated in Figure~\ref{fig:model}.

@@

\mysubsubsection{Relationships to existing methods} Our framework is
general, and it is easy to verify that existing parallel fusion
algorithms are just our special cases.
%
For example, the parallel fusion algorithm by Lempitsky et
al.~\cite{viktor} always performs binary fusion between the current
solution and another label, which can be achieved by setting $\alpha_i =
1$ and $\beta_i = 0$ for all the threads. The algorithm by
Veksler~\cite{olga} or Dejong et al.~\cite{dejong} hierarchically fuses
solutions starting from solution proposals. The algorithm can be
realized by setting $\alpha_i = 1, \beta_i = 0$ initially, then use
$\alpha_i = 0, \beta_i=1$  for the rest of the algorithm.

\noindent
We now illustrate the power of Swarm Fusion framework for three problems
in Computer Vision.

>>>>

Assuming we have $N$ threads $\{T_i | i=1, 2, \cdots, N\}$, each thread
$T_i$ maintains and updates a solution $S_i$ in parallel. Alpha
expansion picks one label in each iteration to perform fusion. FM
invokes one proposal generation scheme and generates a solution proposal
for fusion. Swarm Fusion has 1) a {\it proposal pool}, from which we
pick arbitrary number of proposal generation schemes and generate
proposals, and 2) a {\it solution pool}, from which we pick arbitrary
number of intermediate solutions generated by all the other threads.
%
% Traditional FM has a set of proposal generation schemes to be
% invoked
%
% There are two places to
% collect solutions or solution proposals for fusion. First, the {\it
% proposal pool} can generate new solution proposals on request.
% %
% Second, the {\it solution pool} stores the solutions that have been
% fused by the threads.
In our base configuration, the solution pool only remembers one (the
best) solution generated by each thread.

Swarm Fusion has two main parameters $\alpha_i$ and $\beta_i$ (for each
thread $T_i$), determining the processing flow of the algorithm: In each
fusion step, the thread collects $\alpha_i$ solution proposals from the
proposal pool and $\beta_i$ solutions from the solution pool, following
a user-defined strategy or at random to be simple.
%
% One can further customize how to pick certain proposal generation
% schemes (as in ~\cite{delong}) or solutions.
Swarm Fusion framework is very flexible and yields various data
processing architectures as shown in Figure~\ref{fig:model}.
%
\begin{figure}[tb]
 \includegraphics[width=\columnwidth]{figure/model.pdf} \caption{Swarm
 Fusion architecture and its relationships to existing methods. mention
 that hierarchical fusion works in a different way, but we can still
 consider that to be our special case, by letting each thread not using
 its own solution in the next fusion.}\label{fig:model}
\end{figure}
%
The bottom right configuration is the most general one, in which we
always fuse some solution proposals and some concurrent solutions
(i.e., $\alpha\ne 0, \beta \ne 0$).
%
Each fusion is multi-way (not binary) with a non-submodular energy, and
we use TRW~\cite{kolmogorov} for the fusion, while any other compatible
inference techniques can be used~\cite{opengm}. Of course, if one knows
that a certain fusion step is a binary fusion with submodular energy,
one can use graph-cuts instead~\cite{alpha_expansion_paper}. If a
certain fusion step is a binary fusion with non-submodular energy, one
can use QPBO~\cite{second_order_smoothness_stereo}.
%
Note that the threads are all synchronized in the figure for a
illustration purpose. In practice, all the threads run asynchronously
with a (read-write) lock on the data in the two pools (See Algorithm~\ref{algorithm:sf}).
%The asynchronous processing could be difficult for cloud parallel
%computing.
%
%
%
\begin{algorithm}
 \caption{Swarm Fusion method}
 \label{algorithm:sf}
 \begin{algorithmic}
  %\Procedure{Swarm Fusion method} {}
  \Procedure{} {$\alpha, \beta$}
  \State $\mathcal{S}_{pool} \leftarrow \emptyset$ //
  Solution pool
  \State Initialize $\mathcal{P}_{pool}$ // Proposal pool
  \ForEach{thread $T_i$}
  \State Initialize its solution $S_i$
  \EndFor
  \State
  \ForEach{thread $T_i$ in parallel till convergence}
  \State Pick $\alpha$ solution proposals $\mathcal{P}\subset \mathcal{P_{\mbox{pool}}}$
  \State Pick $\beta$ solutions $\mathcal{S} \subset \mathcal{S_{\mbox{pool}}}$
  \State $S_i \leftarrow \mbox{Fuse}(S_i, \mathcal{P}, \mathcal{S})$
  \State Replaces the solution in $\mathcal{S}_{pool}$ with $S_i$
  \State [ Generates proposals and update $\mathcal{P}_{pool}$ ]
  \EndFor
  \EndProcedure
 \end{algorithmic}
\end{algorithm}

@@

\noindent It is easy to verify that alpha-expansion
(AE)~\cite{alpha_expansion}, fusion move (FM)~\cite{viktor}, parallel
alpha-expansion (PAE)~\cite{delong}, and hierarchical fusion
(HF)~\cite{delong_hierarchical,olga} are all special cases of the Swarm
Fusion method.~\footnote{The hierarchical fusion has a slightly
different data processing model, without strong ties between threads
data, but this can be considered as a special case of SF by not using
$S_i$ in each fusion step of $T_i$.} For example, AE can be realized by
setting $\alpha=1, \beta=0$ and restricting the proposal generation to
constant labels with a single thread. Same goes for FM, this time,
without the restriction on the proposal generation scheme. PAE is
realized by setting $\alpha=1,\beta=1$ with multiple threads, again with
a restriction on the proposal generation scheme. The last sequential
fusion (at the top of the diagram in the figure) can be modeled by
changing to $\alpha=0, \beta=1$ with a single thread.

% The swarm fusion is highly flexible, and we first introduce our base
% architecture that exploits general strenghts offered by the
% framework. Later, we explain how to further optimize the configuration
% to boost performance for specific problems. In the base architecture,
% all the threads fuse some number of proposals from the proposal pool and
% some number of solutions from the solution pool in each step. In other
% words, all the threads constantly exchange solutions while injecting new
% proposals. This architecture is illustrated in Figure~\ref{fig:model}.

@@

% \mysubsubsection{Relationships to existing methods} Our framework is
% general, and it is easy to verify that existing parallel fusion
% algorithms are just our special cases.
%
% For example, the parallel fusion algorithm by Lempitsky et
% al.~\cite{viktor} always performs binary fusion between the current
% solution and another label, which can be achieved by setting $\alpha_i =
% 1$ and $\beta_i = 0$ for all the threads. The algorithm by
% Veksler~\cite{olga} or Dejong et al.~\cite{dejong} hierarchically fuses
% solutions starting from solution proposals. The algorithm can be
% realized by setting $\alpha_i = 1, \beta_i = 0$ initially, then use
% $\alpha_i = 0, \beta_i=1$  for the rest of the algorithm.

% \noindent
% We now illustrate the power of Swarm Fusion framework for three problems
% in Computer Vision.
